Compositional Certified Resource Bounds

### 2015-04-09 paper/main.tex
use scale=1 for the badge
AEC badge will be added later

\usepackage[utf8]{inputenc} %for utf8 input
\usepackage{amssymb} %for shift symbol
\usepackage{amsmath}
\usepackage{listings} %for code
\lstset{moredelim=[is][\color{blue}]{@}{@},keepspaces=true}
\usepackage{mathpartir} %for typing rules
\usepackage{microtype} %better micro typing
\usepackage{stmaryrd} %for llbracket
\usepackage{mathabx} % for boxes
\usepackage{graphicx} %to include png images
\usepackage{xcolor} %for colors
\usepackage{url}
\usepackage{enumitem}
\usepackage{array} %for stupid tables
\usepackage[firstpage]{draftwatermark}
\SetWatermarkText{\hspace*{8in}\raisebox{5.5in}{\includegraphics[width=2.0cm]{fig/aec-badge-pldi.pdf}}}
\SetWatermarkAngle{0}

@@

\authorinfo
{Quentin Carbonneaux \and Jan Hoffmann \and Zhong Shao}
{Yale University \vspace{-1cm}}

@@

\vspace{-.24cm}

>>>>

\usepackage[utf8]{inputenc} %for utf8 input
\usepackage{amssymb} %for shift symbol
\usepackage{amsmath}
\usepackage{listings} %for code
\lstset{moredelim=[is][\color{blue}]{@}{@},keepspaces=true}
\usepackage{mathpartir} %for typing rules
\usepackage{microtype} %better micro typing
\usepackage{stmaryrd} %for llbracket
\usepackage{mathabx} % for boxes
\usepackage{graphicx} %to include png images
\usepackage{xcolor} %for colors
\usepackage{url}
\usepackage{enumitem}
\usepackage{array} %for stupid tables
%\usepackage[firstpage]{draftwatermark}
%\SetWatermarkText{\hspace*{8in}\raisebox{5.5in}{\includegraphics[scale=0.1]{fig/aec-badge-pldi.pdf}}}
%\SetWatermarkAngle{0}

@@

\authorinfo
{Quentin Carbonneaux \and Jan Hoffmann \and Zhong Shao}
{Yale University}
{\{first.last\}@yale.edu}

@@
